
\section{Introduction}
The subject of this report is the procedure of designing and producing a step up converter in the form of a printed circuit board.\
This report will explore the procedures required for developing such a printed circuit board being, choice of components, circuit design, printed circuit board layout, printing the board and testing of the board but also the difficulties and and was was learned throughout the project.\ 
The goal of the project was to successfully produce a step up converter using the tools at hand. But also to get the understanding of some of the difficulties one can encounter in the process.\
jdhfuhdjhdjdfh

\textit{Explain the subject. What was i studying? Why was this topic important to investigate? What did we know about the topic before I did this study? How will this study dvance new knowledge or new ways of understanding?}
\begin{itemize}
    \item Generally known information about the topic
    \item Prior studies' historical context to your research
    \item Your hypothesijks and overview of the results
    \item How the article is organized
\end{itemize}
\subsection{State of the Art}
\textit{The latest and most sophisticated or advanced stage of a technology or science. State of the art if the foundation for determining the methid and methodlogy.}
\subsection{Hypothesis}
\textit{In scienc, a hypothesis is an idea or explanation that you then tesr through study and experimentation. Outside science, a theory or quess can also be called a hypothesis}
\subsection{Research questions}
\textit{A research question guides and centers your research. It should be clear and focusd, as well as synthesize multiple sources to present your unque argument. RQ should be furmulat}
